---
title: "Support Effectiveness Results"
format: 
  html:
    code-fold: true
---

# Initial Preparation

## Load the Pre/post data

```{r load}
#| warning: false
#| message: false
library(tidyverse)
library(lme4)
source("Data/AllMetadata.R")
PPIESFall2022 <- 
  read_csv("Data/PPIESFall2022Full.csv",
           col_types=colAll)
```

## Composite Treatment variables

Note that treatments differ for the ECT and POT subtests, so need to
analyze them separately.

Treatments are marked by the `CognitiveSupports` and `AffectiveECT` or 
`AffectivePOT` variables.

This code shows counts in each condition/ECT Treatment

```{r cond3}
PPIESFall2022 %>%
  mutate(ECTcond=factor(PPIESFall2022$CognitiveSupports+
                        PPIESFall2022$AffectiveECT,0:2,
                        c("Control","COG","COG+AFF"))) %>%
  mutate(POTcond=factor(PPIESFall2022$CognitiveSupports+
                        PPIESFall2022$AffectivePOT,0:2,
                        c("Control","COG","COG+AFF"))) ->
  PPIESFall2022
table(PPIESFall2022$Condition,PPIESFall2022$ECTcond)
```
Condition/POTTreatment

```{r}
table(PPIESFall2022$Condition,PPIESFall2022$POTcond)
```

## Calculate Gain Scores

```{r gains}
PPIESFall2022 %>%
  mutate(NearECTgain=NearECTpost-NearECT,
         FarECTgain=FarECTpost-FarECT,
         ECTgain=ECTpost-ECT,
         NearPOTgain=NearPOTpost-NearPOT,
         FarPOTgain=FarPOTpost-FarPOT,
         POTgain=POTpost-POT) ->
  PPIESFall2022
```

# Were there learning gains?

```{r}
n.POTgain <- sum(!is.na(PPIESFall2022$POTgain))
m.POTgain <- mean(PPIESFall2022$POTgain,na.rm=TRUE)
s.POTgain <- sd(PPIESFall2022$POTgain,na.rm=TRUE)
t.POTgain <- m.POTgain/s.POTgain/sqrt(s.POTgain)
cat("Average POT gain ",round(m.POTgain,2),"(",round(s.POTgain,3),"); t(",
    n.POTgain,")=",t.POTgain,"\n")
n.ECTgain <- sum(!is.na(PPIESFall2022$ECTgain))
m.ECTgain <- mean(PPIESFall2022$ECTgain,na.rm=TRUE)
s.ECTgain <- sd(PPIESFall2022$ECTgain,na.rm=TRUE)
t.ECTgain <- m.ECTgain/s.ECTgain/sqrt(s.ECTgain)
cat("Average ECT gain ",round(m.ECTgain,2),"(",round(s.ECTgain,3),"); t(",
    n.ECTgain,")=",t.ECTgain,"\n")
```


# Graphical Analysis of Pre/Post

## ECT by Condition
```{r}
#| warning: false
ggplot(PPIESFall2022,aes(x=Condition,y=ECTgain,color=ECTcond)) +
  geom_violin() +labs(title="ECT Gain scores")
```
```{r}
#| warning: false
ggplot(PPIESFall2022,aes(x=Condition,y=NearECTgain,color=ECTcond)) +
  geom_violin() + labs(title="ECT Near Transfer")
```
```{r}
#| warning: false
ggplot(PPIESFall2022,aes(x=Condition,y=FarECTgain,color=ECTcond)) +
  geom_violin()  + labs(title="ECT Far Transfer")
```

## POT Exploratory graphics

```{r}
#| warning: false
ggplot(PPIESFall2022,aes(x=Condition,y=POTgain,color=POTcond)) +
  geom_violin() + labs(title="POT Gain Scores")
```

```{r}
#| warning: false
ggplot(PPIESFall2022,aes(x=Condition,y=NearPOTgain,color=POTcond)) +
  geom_violin() + labs(title="POT Near Transfer")
```

```{r}
#| warning: false
ggplot(PPIESFall2022,aes(x=Condition,y=FarPOTgain,color=POTcond)) +
  geom_violin()  + labs(title="POT Far Transfer")
```

# ANCOVA

## ECT

```{r}
ECTlm <- lm(ECTpost ~ ECT+CognitiveSupports+AffectiveECT,data=PPIESFall2022,
            na.action=na.omit)
ECTct <- cbind(coef(summary(ECTlm)),d=coef(ECTlm)/summary(ECTlm)$sigma)
round(ECTct,3)
cat("R-squared: ",round(summary(ECTlm)$r.squared, 3), 
    "; d.f.=", summary(ECTlm)$df[2],"\n")
```

ECT is pretest.
Affective supports are significant, but in the wrong direction.

### Random Effects

Add classroom as a random effect, as there is a considerable age, and scientific
and mathematical sophistication differences.

```{r}
ECTlmer <- lmer(ECTpost ~ ECT+CognitiveSupports+AffectiveECT + (1|Class),
              data=PPIESFall2022, na.action=na.omit)
summary(ECTlmer)
ECTcter <- cbind(coef(summary(ECTlmer)),d=fixef(ECTlmer)/summary(ECTlmer)$sigma)
round(ECTcter,3)
```


## POT

```{r}
POTlm <- lm(POTpost ~ POT+CognitiveSupports+AffectivePOT,data=PPIESFall2022,
            na.action=na.omit)
POTct <- cbind(coef(summary(POTlm)),d=coef(POTlm)/summary(POTlm)$sigma)
round(POTct,3)
cat("R-squared: ",round(summary(POTlm)$r.squared, 3), 
    "; d.f.=", summary(POTlm)$df[2],"\n")

```

No significant effects of supports.
### Random Effects

Add classroom as a random effect, as there is a considerable age, and scientific
and mathematical sophistication differences.

```{r}
POTlmer <- lmer(POTpost ~ POT+CognitiveSupports+AffectivePOT + (1|Class),
              data=PPIESFall2022, na.action=na.omit)
summary(POTlmer)
POTcter <- cbind(coef(summary(POTlmer)),d=fixef(POTlmer)/summary(POTlmer)$sigma)
round(POTcter,3)
```
## Notes from the data collection

1. General energy and excitement was high, so probably no need for affective supports.

2. Students worked in tables of up to 4 students.  Considerable talk with students.

3. Students were supposed to wear earphones to hear audio on video clips, but compliance was low.

4. Students were frequently observed looking around the room and talking to their peers while support videos were playing.

## Levels Solved

```{r}
PPIESFall2022 %>% mutate(solved=silver.max+gold.max) -> PPIESFall2022

```

```{r}
ggplot(PPIESFall2022,aes(x=Condition,y=solved,color=POTcond)) +
  geom_violin()  + labs(title="Levels Solved")
```

```{r}
table(PPIESFall2022$Condition,PPIESFall2022$solved)
```

Something screwy is happening with condition B.  I need to look more closely.