---
title: "Affective Support Data"
---

# Data from the Affective Support Study

The complete data are available in the following formats:

* [Comma Separated Value](Data/PPIESFall2022Full.csv)
* [SPSS Save file](Data/PPIESFall2022BigDaddy.sav)

Metadata are available using the [readr](https://readr.tidyverse.org/) `cols` format in
this [R metadata all script](Data/AllMetadata.R).

The following steps will load the file using the metadata in R.
```{r ReadAll}
#| eval: false
library(readr)
source("https://pluto.coe.fsu.edu/PhysicsDataPlayground/Data/AllMetadata.R")
PPIESFall2022Full <- 
  read_csv("https://pluto.coe.fsu.edu/PhysicsDataPlayground/Data/PPIESFall2022Full.csv",
           col_types=colAll)
```


## Pretest, Posttest, demographic and Questionnaire data

This data subset contains just the data from the pretest and posttest questionnaires.

Posttest columns are marked with either `.ect` or `.pot` depending on which
posttest the items appear on.  Note that students received the ECT and POT 
tests on Wednesday or Friday of the study week depending on their treatment group.

[Pre, Post Data](Data/PPIESFall2022PrePost.csv)


The `readr::cols` metadata is in [Pre-post R metadata script]("https://pluto.coe.fsu.edu/PhysicsDataPlayground/Data/PrePostMetadata.R").

```{r ReadPP}
#| eval: false
library(readr)
source("https://pluto.coe.fsu.edu/PhysicsDataPlayground/Data/PrePostMetadata.R")
PPIESFall2022PrePost <- 
  read_csv("https://pluto.coe.fsu.edu/PhysicsDataPlayground/Data/PPIESFall2022PrePost.csv",
           col_types=colPrePost)
```

An alternative version of the PrePost data which replaces the text of the options for the
raw responses, with the codes A, B, C, and D.
[Pre, Post Data ABC coding](Data/PPIESFall2022PrePostABC.csv)

Here is the [Recoding Script](scripts/RecodeRawData.R).

The `readr::cols` metadata is in [Pre-post ABC coding R metadata script]("https://pluto.coe.fsu.edu/PhysicsDataPlayground/Data/PrePostMetadataABC.R").

```{r ReadPPABC}
#| eval: false
library(readr)
source("https://pluto.coe.fsu.edu/PhysicsDataPlayground/Data/PrePostMetadataABC.R")
PPIESFall2022PrePostABC <- 
  read_csv("https://pluto.coe.fsu.edu/PhysicsDataPlayground/Data/PPIESFall2022PrePostABC.csv",
           col_types=colPrePost)
```

## Game level outcome data

These data contain information on how the learning supports were played.
* `Timestamp_XXX` -- These give the time at which the level was played.
* `TrophyLevel_XXX` -- what trophy the player earned.  This can be `gold`,
`silver`, `quit` or missing.  The `quit` indicates that the player attempted
the level but did not earn a trophy.
* `NumberAttempts_XXX` -- The number of attempts the player made for this game level.

Note that the player may have attempted each level several times.  There 
are three versions of this data file, one showing the values related to the
first level (`.first`), one to the last levels (`.last) and one showing the best 
trophy recieved (`.max).  In the full data set the suffixes
`.first`, `.last`, and `.max` are added to the column names to indicate which
version is used.

* [Observables, First Attempt](Data/PPIESFall2022obsFirst.csv)
* [Observables, Last Attempt](Data/PPIESFall2022obsLast.csv)
* [Trophies Only, Last Attempt](Data/PPIESFall2022obsMax.csv)

The `readr::cols` metadata is in [Observables R metadata script]("https://pluto.coe.fsu.edu/PhysicsDataPlayground/Data/ObsMetadata.R").

```{r ReadObs}
#| eval: false
library(readr)
source("https://pluto.coe.fsu.edu/PhysicsDataPlayground/Data/ObsMetadata.R")
PPIESFall2022obsFirst <-
  read_csv("https://pluto.coe.fsu.edu/PhysicsDataPlayground/Data/FSUSFall2022obsFirst.csv",
            col_types=colObsFirst)
PPIESFall2022obsLast <-
  read_csv("https://pluto.coe.fsu.edu/PhysicsDataPlayground/Data/FSUSFall2022obsFirst.csv",
            col_types=colObsLast)
PPIESFall2022obsMax <-
  read_csv("https://pluto.coe.fsu.edu/PhysicsDataPlayground/Data/FSUSFall2022obsFirst.csv",
            col_types=colObsMax)
```


## Learning support usage data

This is data about the usage of the learning supports.

[Learning Support](Data/PPIESFall2022ls.csv)

The `readr::cols` metadata is in [Learning Support R metadata script]("https://pluto.coe.fsu.edu/PhysicsDataPlayground/Data/LSMetadata.R").

```{r ReadLS}
#| eval: false
library(readr)
source("https://pluto.coe.fsu.edu/PhysicsDataPlayground/Data/LSMetadata.R")
PPIESFall2022ls <- 
  read_csv("https://pluto.coe.fsu.edu/PhysicsDataPlayground/Data/PPIESFall2022ls.csv",
           col_types=colLS)
```


## Bayesian network scores

This provides scores from the Bayesian Network model, which probabilities
for the nine nodes in the competency model.  For each none, there are three
columns giving the marginal probability of the `High`, `Medium` and `Low`
proficiency respectively.  The `EAP` (expected a posteriori) scores are
produced by assigning `Low=-1`, `Medium=0` and `High=1` and calculating the
expected value.

[Bayesian Network Scores](Data/PPIESFall2022BN.csv)

The `readr::cols` metadata is in [Pre-post R metadata script]("https://pluto.coe.fsu.edu/PhysicsDataPlayground/Data/PrePostMetadata.R").

```{r ReadBN}
#| eval: false
library(readr)
source("https://pluto.coe.fsu.edu/PhysicsDataPlayground/Data/PrePostMetadata.R")
PPIESFall2022BN <- 
  read_csv("https://pluto.coe.fsu.edu/PhysicsDataPlayground/Data/PPIESFall2022BN.csv",
           col_types=colBN)
```


## Log files

The raw JSON data is available at
<https://pluto.coe.fsu.edu/PhysicsPlayground/data/IES2022-AllP4Events.json.gz>

The filtered data containing only “interesting” events is at:
<https://pluto.coe.fsu.edu/PhysicsPlayground/data/PPIES2022-P4Filtered.json.gz>

Both files are compressed using gnu zip (gzip)

