---
title: "Event Logs"
---

## Proc4 and xAPI formats

Events are stored in the Proc 4 format [@ralmond2019a].  It is converted from the 
xAPI [@xAPI] format using in Learning Locker [@LearningLocker] by the dongle code 
in the Proc4 [@Proc4] package.  In particular, it means that messages are identified by
`(verb, object)` pairs (xAPI-style) not single `mess` strings (Proc4-style)

The JSON format is as follows:

```json
{
  app: "ecd://epls.coe.fsu.edu/PhysicsPlayground/IES/Fall22/BigStudy",  /* Fixed String */
  uid: "[A-F]0000",
  context: "Game Level",
  sender: "PP Learning Locker",  /* Fixed String */
  verb: <<see event vocabulary>>, 
  object <<see event vocabulary>>, 
  timestamp: POSIX time string, /* When event was logged. */
  processed: logical,  /* For internal EI use */
  pErr: string, /* Error code from processing (if any) */
  data: { <<Arbitrary JSON document>>}
}
```


 The `app` and `sender` strings are constant, so are probably not interesting.

The first character of the `uid` gives the study condition.


## Table of known verbs and objects

The master list of levels: <Data/LevelData.csv>

The list of all verb--object pairs:  <Data/EventTable.csv>

### Object List 

```{r}
objectList <- c("game level", "silverWin", "game object", "learning support",
                "goldWin", "newPurchase", "newMoneyEarned", "replayButton",
                "game (Physics Playground)", "ball", "footBall",
                "billiardStripeBall", "glossary", "definition", "golfBall",
                "formula", "module")
objectList
```

### Object Type

These are the values of the `gemeObjectType` [sic] field, indicating the type of object
from the object classification system.

```{r objectType}
objectTypes <- c("freeform", "Ramp", "Lever", "ball", "pin", "Pendulum",
                 "Springboard","Weight")
objectTypes
```


## Links to data

The raw JSON data is available at
<https://pluto.coe.fsu.edu/PhysicsPlayground/data/IES2022-AllP4Events.json.gz>

The filtered data containing only “interesting” events is at:
<https://pluto.coe.fsu.edu/PhysicsPlayground/data/PPIES2022-P4Filtered.json.gz>

Both files are compressed using gnu zip (`gzip`)

