---
title: "Efficacy Study Pre/Post Item Analysis"
format: 
  html:
    code-fold: true
---

```{r}
library(tidyverse)
library(ShinyItemAnalysis)
library(psych)
library(mirt)
```



```{r ReadPPABC}
source("Data/PrePostMetadataABC.R")
PrePostABC <- 
  read_csv("Data/PPIESFall2022PrePostABC.csv", col_types=colPrePostABC)
ppKeys <- readr::read_csv("Instruments/KeysAndCodes_Physics.csv")
source("Data/BAMetadata.R")
BAdata <- 
  read_csv("Data/BAdata.csv",   col_types=colBAdata)
```
Questions ANQ12, 13 and 14 were included erroneously on ect posttest.
Remove them.

```{r}
PrePostABC <- select(PrePostABC,!matches("A-NQ1[2-4](_scored)?.ect"))
grep("A-NQ[0-9]+.ect",names(PrePostABC),value=TRUE)
```



```{r}
preraw <- select(PrePostABC,`A-NQ1`:`A-FQ14`)
itemnames <- names(preraw)
prescored <- select(PrePostABC,`A-NQ1_scored`:`A-FQ14_scored`)
names(prescored) <- sub("_scored","",names(prescored))
postraw <- select(PrePostABC,matches("A-.Q[0-9]+\\.(ect|pot)"))
names(postraw) <- sub("\\.(ect|pot)","",names(postraw))
postscored <- select(PrePostABC,matches("A-.Q[0-9]+\\_scored.(ect|pot)"))
names(postscored) <- sub("_scored\\.(ect|pot)","",names(postscored))
```

Before/After data is trickier as People got Form A or B for the pre/posttest.

```{r}
BAdataA <- BAdata[BAdata$Pre_Form=="A",]
BAdataB <- BAdata[BAdata$Pre_Form=="B",]
```

Now make naming conventions match.
```{r}
names(BAdataA)[30:43]<-paste("A-NQ",1:14,sep="")
names(BAdataB)[30:43]<-paste("B-NQ",1:14,sep="")
names(BAdataA)[44:57]<-paste("A-FQ",1:14,sep="")
names(BAdataB)[44:57]<-paste("B-FQ",1:14,sep="")
names(BAdataA)[58:71]<-paste("B-NQ",1:14,sep="")
names(BAdataB)[58:71]<-paste("A-NQ",1:14,sep="")
names(BAdataA)[72:85]<-paste("B-FQ",1:14,sep="")
names(BAdataB)[72:85]<-paste("A-FQ",1:14,sep="")
```

Repackage into Form A and Form B (lumping pre- and posttest together).

```{r}
formA <- rbind(select(BAdataA,Pre_Form,starts_with("A-")),
               select(BAdataB,Pre_Form,starts_with("A-")))
formB <- rbind(select(BAdataA,Pre_Form,starts_with("B-")),
               select(BAdataB,Pre_Form,starts_with("B-")))
```

Finally, split out form A and B keys (also covert to upper as used in raw data).

```{r}
formAkeys <- toupper(ppKeys$Key[ppKeys$Form=="A"])
formBkeys <- toupper(ppKeys$Key[ppKeys$Form=="B"])
```


## Pretest Item Analysis

```{r}
prealpha <- psych::alpha(prescored)
postalpha <- psych::alpha(postscored)
formAalpha <- psych::alpha(formA[,-1])
formBalpha <- psych::alpha(formB[,-1])
```

### Reliabilities

Cronbach's alpha for the various forms.

```{r}
cat("Timing Study Form A", round(formAalpha$total[[2]],3),"\n")
cat("Timing Study Form B", round(formBalpha$total[[2]],3),"\n")
cat("Efficacy Study Pretest", round(prealpha$total[[2]],3),"\n")
cat("Efficacy Study Posttest", round(postalpha$total[[2]],3),"\n")
```
## Efficacy Pretest Difficulties and Discriminations

```{r}
#| fig-cap: "Item summaries Efficacy Study Pretest"
DDplot(prescored)
```

## Efficacy Posttest Difficulties and Discriminations

```{r}
#| fig-cap: "Item summaries Efficacy Study Posttest"
DDplot(postscored)
```

## Timing Study Form A Difficulties and Discriminations

```{r}
#| fig-cap: "Item summaries Timing Study Form A (Pre+Post)"
DDplot(formA[,-1])
```

## Timing Study Form B Difficulties and Discriminations

```{r}
#| fig-cap: "Item summaries Timing Study Form B (Pre+Post)"
DDplot(formB[,-1])
```


## Item by Item

```{r}
itemStats <- function (iname) {
  res <- rbind(pretest=prealpha$item.stats[iname,c(1,4,6,7)],
               posttest=postalpha$item.stats[iname,c(1,4,6,7)],
               formA=formAalpha$item.stats[iname,c(1,4,6,7)])
  cbind(res,alpha.drop=c(prealpha$alpha.drop[iname,2],
                         postalpha$alpha.drop[iname,2],
                         formAalpha$alpha.drop[iname,2]))
}                         
istats <- map(names(prescored),itemStats)
names(istats) <- names(prescored)
```


```{r}
da <- DistractorAnalysis(preraw,formAkeys,num.groups = 6)
pda <- function(item) plotDistractorAnalysis(preraw,formAkeys,num.groups=6,
                                             item=item)[[1]]
```


### Distractor Analysis ECT Near

::: {.panel-tabset}

### A-NQ1

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-NQ1"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```

### A-NQ2

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-NQ2"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```
### A-NQ3

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-NQ3"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```
### A-NQ4

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-NQ4"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```
### A-NQ5

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-NQ5"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```
### A-NQ6

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-NQ6"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```

### A-NQ7

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-NQ7"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```
:::

### Distractor Analysis POT Near

::: {.panel-tabset}

### A-NQ9

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-NQ9"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```
### A-NQ10

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-NQ10"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```

### A-NQ11

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-NQ11"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```

### A-NQ12

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-NQ12"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```

### A-NQ13

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-NQ13"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```

### A-NQ14

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-NQ14"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```

:::



### Distractor Analysis ECT Far

::: {.panel-tabset}

### A-FQ1

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-FQ1"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```

### A-FQ2

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-FQ2"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```
### A-FQ3

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-FQ3"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```
### A-FQ4

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-FQ4"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```
### A-FQ5

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-FQ5"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```
### A-FQ6

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-FQ6"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```
### A-FQ7

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-FQ7"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```

### A-FQ8

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-FQ8"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```
:::

### Distractor Analysis POT Far

::: {.panel-tabset}

### A-FQ9

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-FQ9"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```
### A-FQ10

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-FQ10"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```

### A-FQ11

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-FQ11"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```

### A-FQ12

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-FQ12"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```

### A-FQ13

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-FQ13"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```

### A-FQ14

```{r}
#| tbl-subcap: 
#|  - "Item Analysis"
#|  - "Counts"
#| layout-ncol: 2
item <- "A-FQ14"
knitr::kable(istats[[item]],digits=2)
knitr::kable(da[[item]])
```
```{r}
pda(item)
```

:::

